---
title: "11-13_adolescents_100824"
author: "Bella moger"
date: "2024-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


rm(list=ls())

# Load Packages
```{r}
library(tidyverse)## Always load tidyverse
library(skimr) ## Used to summarize our dataframe
library(corrplot) ## correlograms
library(psycho) ## dprime
#install.packages("MatchIt")
library(MatchIt) ## Matching with caliper
```


#load in data
```{r}

## Set path
path <- "/Users/bellamoger/Documents/GitHub/SPARK/"

## Load in
stim <- read.csv(paste0(path, "elizabetheberts_adolescent_faces_r01_faceratings_raw_2404041231.csv"))

## Investigate the variables we kept
summary(stim)

```

# Prepping encoding dataframe and looking at distributions

```{r}
encoding <- stim %>%
  filter(trialcode == "encoding") %>%
  mutate(imagetype_vote = recode(response,
                                 `33` = "child",
                                 `36` = "not_child"))

## Looking at distributions
encoding %>% 
  group_by(subject, imagetype_vote) %>% 
  tally() %>% 
  pivot_wider(names_from = imagetype_vote, values_from = n) %>% 
  mutate(across(everything(), replace_na, replace = 0)) %>% 
  ggplot()+
  geom_density(aes(x = child, color = "child", fill = "child"), alpha = 0.1) +
  geom_density(aes(x = not_child, color = "not_child", fill = "not_child"), alpha = 0.1) +
  labs(x = "Number of Votes for Each Type per Person", y = "Density", title = "Distributions of Responses") +
  theme_classic()


## Making violin dotplots to see discrete people

library(reshape2)

encoding %>% 
  group_by(subject, imagetype_vote) %>% 
  tally() %>% 
  pivot_wider(names_from = imagetype_vote, values_from = n) %>% 
  mutate(across(everything(), replace_na, replace = 0)) %>% 
  select(subject, child, not_child) %>% 
  reshape2::melt() %>%
  ggplot(aes(x = variable, y = value, fill = variable)) +
  geom_boxplot(notch = TRUE, alpha  = .5, outlier.shape = NA) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1.7, binwidth = .9999999, stackratio=1.8, alpha = .9)+
  labs(x = "Response", y = "Number of Votes of Each Type", title = "Distributions of Responses") +
  scale_fill_discrete(name = "Column") +
  theme_classic() +
  theme(legend.position = "none")
```


# Prepping recall dataframe and looking at distributions

```{r}
recall <- stim %>% 
  filter(str_detect(trialcode, "rating")) %>% 
  mutate(memory = recode(response,
                         `0` = "definitely_old",
                         `1` = "maybe_old",
                         `2` = "maybe_new",
                         `3` = "definitely_new"))

#Looking at distributions
recall %>% 
  group_by(subject, memory) %>% 
  tally() %>% 
  pivot_wider(names_from = memory, values_from = n) %>% 
  mutate(across(everything(), replace_na, replace = 0)) %>% 
  select(subject, definitely_old, maybe_old, maybe_new, definitely_new) %>% 
  reshape2::melt() %>%
  ggplot(aes(x = variable, y = value, fill = variable)) +
  geom_boxplot(notch = TRUE, alpha  = .5, outlier.shape = NA) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1.5, binwidth = 4.9999999, stackratio=1.7, alpha = .9)+
  labs(x = "Response", y = "Number of Votes per Image", title = "Distributions of Responses") +
  scale_fill_discrete(name = "Column") +
  scale_y_continuous(limits = c(0,475), 
                     breaks = c(0,100,200,300,400,473))+
  theme_classic() +
  theme(legend.position = "none")
```


#divide per subject
```{r}

rating_counts <- encoding %>% 
  count(stimulusitem1, imagetype_vote) %>%
  pivot_wider(names_from = imagetype_vote, values_from = n, values_fill = 0) %>% 
  mutate(pct_endorsed_child = child/(child+not_child)) %>%
  mutate(across(everything(), ~ replace(., is.nan(.), NA))) %>% 
  select(stimulusitem1, pct_endorsed_child) %>% 
  rename(image_name = stimulusitem1)

```


#take previous data file created, and manually remove all faces that were used... load back in
```{r}

## Set path
path <- "/Users/bellamoger/Documents/GitHub/SPARK/11-15 faces/"

## Load in
stimuli.work <- read.csv(paste0(path, "notused_stimuli.csv")) 

# look at distributions
stimuli.work %>% 
  ggplot()+
  geom_density(aes(x = pct_endorsed_child, color = "pct_endorsed_child", fill = "pct_endorsed_child"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "Value", y = "Density", title = "Percent Endorsed") +
  theme_classic()

## Distribution of different d' memorability scores accross all images
stimuli.work %>% 
  ggplot()+
  geom_density(aes(x = general_dprime, 
                   color = "general_dprime", fill = "general_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_treshold_dprime, 
                   color = "highconfidence_treshold_dprime", fill = "highconfidence_treshold_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_subset_dprime, 
                   color = "highconfidence_subset_dprime", fill = "highconfidence_subset_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "d'", y = "Density", title = "Memorability (d')") +
  theme_classic()
```

#how many faces looked OLDER than 9-13? 
#check for >13 year olds (age_rating)
```{r}
summary(stimuli.work)
older <-subset(stimuli.work,age_rating>13)

# look at distributions
older %>% 
  ggplot()+
  geom_density(aes(x = pct_endorsed_child, color = "pct_endorsed_child", fill = "pct_endorsed_child"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "Value", y = "Density", title = "Percent Endorsed") +
  theme_classic()

## Distribution of different d' memorability scores accross all images
stimuli.work %>% 
  ggplot()+
  geom_density(aes(x = general_dprime, 
                   color = "general_dprime", fill = "general_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_treshold_dprime, 
                   color = "highconfidence_treshold_dprime", fill = "highconfidence_treshold_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_subset_dprime, 
                   color = "highconfidence_subset_dprime", fill = "highconfidence_subset_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "d'", y = "Density", title = "Memorability (d')") +
  theme_classic()
```


# Filtering out memorability outliers
Remove anyone two standard deviations away on any of our d' scores. 
```{r}
## Filter: keep anything where difference from mean does not exceed 2 SDs
contenders <- stimuli.work %>%
  filter(general_dprime > 0) %>%  ## NEW
  filter(abs(general_dprime - mean(general_dprime)) <= 2 * sd(general_dprime),
         abs(highconfidence_treshold_dprime - mean(highconfidence_treshold_dprime)) <= 2 * sd(highconfidence_treshold_dprime),
         abs(highconfidence_subset_dprime - mean(highconfidence_subset_dprime)) <= 2 * sd(highconfidence_subset_dprime)) 


#I WANT TO DOWNLOAD THE "CONTENDERS"


## How many of each are left? 
table(contenders$door_or_face)
sort(table(contenders$image_type), decreasing = TRUE)

## How many of each face? 
contenders %>% 
  filter(door_or_face == "face") %>% 
  group_by(type) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% View()
```



#11,12,13 not used?
```{r}

```
#final # --> goal age range = 11-15 y/o






