---
title: "adolescent_050724"
output: html_document
date: "2024-05-07"
author: Camille Johnston, edited by Bella Moger
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
summary(cars)
```


# clear history
rm(list=ls())

# Load Packages

```{r}
library(tidyverse)## Always load tidyverse
library(skimr) ## Used to summarize our dataframe
library(corrplot) ## correlograms
library(psycho) ## dprime
#install.packages("MatchIt")
library(MatchIt) ## Matching with caliper
```


# Load in data

```{r}

## Set path
path <- "/Users/bellamoger/Documents/GitHub/SPARK/"

## Load in
stim <- read.csv(paste0(path, "elizabetheberts_adolescent_faces_r01_faceratings_raw_2404041231.csv"))

## Investigate the variables we kept
summary(stim)
```


# Prepping encoding dataframe and looking at distributions

```{r}
encoding <- stim %>%
  filter(trialcode == "encoding") %>%
  mutate(imagetype_vote = recode(response,
                                 `33` = "child",
                                 `36` = "not_child"))

## Looking at distributions
encoding %>% 
  group_by(subject, imagetype_vote) %>% 
  tally() %>% 
  pivot_wider(names_from = imagetype_vote, values_from = n) %>% 
  mutate(across(everything(), replace_na, replace = 0)) %>% 
  ggplot()+
  geom_density(aes(x = child, color = "child", fill = "child"), alpha = 0.1) +
  geom_density(aes(x = not_child, color = "not_child", fill = "not_child"), alpha = 0.1) +
  labs(x = "Number of Votes for Each Type per Person", y = "Density", title = "Distributions of Responses") +
  theme_classic()


## Making violin dotplots to see discrete people

library(reshape2)

encoding %>% 
  group_by(subject, imagetype_vote) %>% 
  tally() %>% 
  pivot_wider(names_from = imagetype_vote, values_from = n) %>% 
  mutate(across(everything(), replace_na, replace = 0)) %>% 
  select(subject, child, not_child) %>% 
  reshape2::melt() %>%
  ggplot(aes(x = variable, y = value, fill = variable)) +
  geom_boxplot(notch = TRUE, alpha  = .5, outlier.shape = NA) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1.7, binwidth = .9999999, stackratio=1.8, alpha = .9)+
  labs(x = "Response", y = "Number of Votes of Each Type", title = "Distributions of Responses") +
  scale_fill_discrete(name = "Column") +
  theme_classic() +
  theme(legend.position = "none")
```


# Prepping recall dataframe and looking at distributions

```{r}
recall <- stim %>% 
  filter(str_detect(trialcode, "rating")) %>% 
  mutate(memory = recode(response,
                         `0` = "definitely_old",
                         `1` = "maybe_old",
                         `2` = "maybe_new",
                         `3` = "definitely_new"))

#Looking at distributions
recall %>% 
  group_by(subject, memory) %>% 
  tally() %>% 
  pivot_wider(names_from = memory, values_from = n) %>% 
  mutate(across(everything(), replace_na, replace = 0)) %>% 
  select(subject, definitely_old, maybe_old, maybe_new, definitely_new) %>% 
  reshape2::melt() %>%
  ggplot(aes(x = variable, y = value, fill = variable)) +
  geom_boxplot(notch = TRUE, alpha  = .5, outlier.shape = NA) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=1.5, binwidth = 4.9999999, stackratio=1.7, alpha = .9)+
  labs(x = "Response", y = "Number of Votes per Image", title = "Distributions of Responses") +
  scale_fill_discrete(name = "Column") +
  scale_y_continuous(limits = c(0,475), 
                     breaks = c(0,100,200,300,400,473))+
  theme_classic() +
  theme(legend.position = "none")
```


# Merge dataframes and count hits, misses, etc. 

```{r}
stimuli_alltrials <- encoding %>% 
  select(subject, stimulusitem1, imagetype_vote) %>% 
  right_join(recall, by = c("subject", "stimulusitem1")) %>% 
  mutate(general = case_when(
    !is.na(imagetype_vote) & str_detect(memory, "old") ~ "general_hit",
    is.na(imagetype_vote) & str_detect(memory, "old") ~ "general_fa",
    !is.na(imagetype_vote) & str_detect(memory, "new") ~ "general_miss",
    is.na(imagetype_vote) & str_detect(memory, "new") ~ "general_cr",
    TRUE ~ NA_character_
  )) %>% 
  mutate(highconfidence = case_when(
    !is.na(imagetype_vote) & memory == "definitely_old" ~ "highconfidence_hit",
    is.na(imagetype_vote) & !str_detect(memory, "definitely_new") ~ "highconfidence_fa",
    !is.na(imagetype_vote) & !str_detect(memory, "definitely_old") ~ "highconfidence_miss",
    is.na(imagetype_vote) & memory == "definitely_new" ~ "highconfidence_cr",
    TRUE ~ NA_character_
  ))
```


# Add dprime scores

```{r}
## General dprime
general_counts <- stimuli_alltrials %>%
  count(stimulusitem1, general) %>%
  pivot_wider(names_from = general, values_from = n, values_fill = 0) %>% 
  mutate(general_dprime = psycho::dprime(general_hit, general_fa, general_miss, general_cr)$dprime) %>% 
  select(stimulusitem1, general_dprime)%>% 
  rename(image_name = stimulusitem1)

## Threshold high confidence (unless endorsed with confidence, its a miss/false alarm)
highconfidence_counts <- stimuli_alltrials %>%
  count(stimulusitem1, highconfidence) %>%
  pivot_wider(names_from = highconfidence, values_from = n, values_fill = 0) %>% 
  mutate(highconfidence_treshold_dprime = 
           psycho::dprime(highconfidence_hit, highconfidence_fa, highconfidence_miss, highconfidence_cr)$dprime) %>% 
  select(stimulusitem1, highconfidence_treshold_dprime)%>% 
  rename(image_name = stimulusitem1)

## Subset high confidence (calculate with only trials that were endorsed with high confidence)
subsethighconfidence_counts <- stimuli_alltrials %>%
  filter(str_detect(memory, "definitely")) %>% 
  count(stimulusitem1, highconfidence) %>%
  pivot_wider(names_from = highconfidence, values_from = n, values_fill = 0, names_prefix = "subset") %>% 
  mutate(highconfidence_subset_dprime = 
           psycho::dprime(subsethighconfidence_hit, subsethighconfidence_fa, 
                          subsethighconfidence_miss, subsethighconfidence_cr)$dprime) %>% 
  select(stimulusitem1, highconfidence_subset_dprime)%>% 
  rename(image_name = stimulusitem1)
```


# Make counts of votes for each image (single vs. double; child vs. no child)

```{r}
rating_counts <- encoding %>% 
  count(stimulusitem1, imagetype_vote) %>%
  pivot_wider(names_from = imagetype_vote, values_from = n, values_fill = 0) %>% 
  mutate(pct_endorsed_child = child/(child+not_child)) %>%
  mutate(across(everything(), ~ replace(., is.nan(.), NA))) %>% 
  select(stimulusitem1, pct_endorsed_child) %>% 
  rename(image_name = stimulusitem1)
```

# Load in demographic info

```{r}
face_info <- read.csv(file.choose()) %>% 
  select(image_name, gender, race, age_group, age_rating,
         contains("ISSUES")) %>% 
  rename(type = race)

## Load additional face info
face_info <- read.csv("/Users/bellamoger/Documents/SPARK/demographics_real.csv") %>% 
  select(image_name, gender, race, age_group, age_rating, contains("ISSUES")) %>% 
  rename(type = race)
```

# Merge all data frames

```{r}
## Make list of dataframes
data_frames <- list(rating_counts, general_counts, highconfidence_counts, subsethighconfidence_counts)

## Join, make new variable, and reorder
stimuli <- reduce(data_frames, full_join, by = "image_name") %>% 
  left_join(face_info, by = "image_name") %>% 
  mutate(image_type = paste(gender, type, sep = "_")) %>% 
  select(image_name, image_type, gender, type, everything()) 
```

### ok going to try to reload in updated file (051224)

```{r}

## Set path
path <- "/Users/bellamoger/Documents/SPARK/"

## Load in
stimuli.work <- read.csv(paste0(path, "stimuli_051224.csv")) 

# look at distributions
stimuli.work %>% 
  ggplot()+
  geom_density(aes(x = pct_endorsed_child, color = "pct_endorsed_child", fill = "pct_endorsed_child"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "Value", y = "Density", title = "Percent Endorsed") +
  theme_classic()

## Distribution of different d' memorability scores accross all images
stimuli.work %>% 
  ggplot()+
  geom_density(aes(x = general_dprime, 
                   color = "general_dprime", fill = "general_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_treshold_dprime, 
                   color = "highconfidence_treshold_dprime", fill = "highconfidence_treshold_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_subset_dprime, 
                   color = "highconfidence_subset_dprime", fill = "highconfidence_subset_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "d'", y = "Density", title = "Memorability (d')") +
  theme_classic()
```


## Create a list of variable names to use in correlation plots
```{r}
dprime_list <- c("general_dprime", "highconfidence_treshold_dprime", "highconfidence_subset_dprime")

## Distribution of memorability scores across genders
#for (variable in dprime_list) {
#  plot <- stimuli %>% 
#    ggplot(aes(x=!!sym(variable), fill=gender)) +
#    geom_density(alpha=0.2)+
#    theme_classic()
#  print(plot)
```


# Filtering out memorability outliers
Remove anyone two standard deviations away on any of our d' scores. 
```{r}
## Filter: keep anything where difference from mean does not exceed 2 SDs
contenders <- stimuli.work %>%
  filter(general_dprime > 0) %>%  ## NEW
  filter(abs(general_dprime - mean(general_dprime)) <= 2 * sd(general_dprime),
         abs(highconfidence_treshold_dprime - mean(highconfidence_treshold_dprime)) <= 2 * sd(highconfidence_treshold_dprime),
         abs(highconfidence_subset_dprime - mean(highconfidence_subset_dprime)) <= 2 * sd(highconfidence_subset_dprime)) 


## How many of each are left? 
table(contenders$door_or_face)
sort(table(contenders$image_type), decreasing = TRUE)

## This group has a wide range of child endorsement (mean __ endorse child)
summary(contenders$pct_endorsed_child)

## How many of each color door? 
contenders %>% 
  filter(door_or_face == "face") %>% 
  group_by(type) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% View()
```



# Picking faces more highly endorsed as looking like child (9-13 y/o)

Now that we have gotten rid of images that are either too memorable or not memorable enough, 
let's pick faces who look most like child of our target age range within each group. 
When we need tie breakers, let's remove faces that had more SDN endorsement of looking fake, and/or any other issues

```{r}
## Filtering top 11 most child faces per group, using SDN ratings and relative high or low dprime as tiebreakers
face_contenders <- contenders %>% 
  filter(door_or_face == "face") %>% 
  group_by(image_type) %>%
  top_n(11, pct_endorsed_child) %>% ## NEW
  top_n(11, -ISSUES_lookfake) %>% ## NEW
  arrange(desc(pct_endorsed_child), ISSUES_SUM) %>% 
  slice_head(n = 11) %>% ## NEW
  ungroup() %>% 
    arrange(desc(general_dprime)) %>% ## NEW
  slice_head(n = 86) %>% ## NEW
  slice_tail(n = 84) ## NEW

## Should have 10-11 of each by now
table(face_contenders$image_type)
table(face_contenders$gender)

## Mean child before and after
#contenders %>% ## BEFORE
face_contenders %>% ## AFTER
  filter(door_or_face == "face") %>% 
  group_by(image_type) %>% 
  summarize(pct_endorsed_child = mean(pct_endorsed_child))

## Very few images now have any endorsement from us about looking fake 
table(face_contenders$image_type, face_contenders$ISSUES_lookfake)
```

# Looking at some new distributions

```{r}
## Distribution of memorability scores across genders
for (variable in dprime_list) {
  plot <- face_contenders %>% 
    ggplot(aes(x=!!sym(variable), fill=gender)) +
    geom_density(alpha=0.2)+
    theme_classic()
  print(plot)
}

## Amoung those we kept, did initial age group seem to make a difference
face_contenders %>% 
  ggplot(aes(x=pct_endorsed_child, fill=age_group)) +
  geom_density(alpha=0.2)+
  theme_classic()
```


# Any differences in memorability between gender? 

```{r}
## General d'
var.test(face_contenders$general_dprime ~ face_contenders$gender, paired = FALSE) 
t.test(face_contenders$general_dprime ~ face_contenders$gender, paired = FALSE, var.equal = TRUE) 

## Threshold high confidence
var.test(face_contenders$highconfidence_treshold_dprime ~ face_contenders$gender, paired = FALSE) 
t.test(face_contenders$highconfidence_treshold_dprime ~ face_contenders$gender, paired = FALSE, var.equal = TRUE)  

## Subset high confidence
var.test(face_contenders$highconfidence_subset_dprime ~ face_contenders$gender, paired = FALSE) 
t.test(face_contenders$highconfidence_subset_dprime ~ face_contenders$gender, paired = FALSE, var.equal = TRUE)
```

# Let's prepare to match with the doors now!

```{r}
## Merge back in just our door contenders, and make our "treatment" variable
contenders_facesfinalized <- contenders %>% 
  filter(door_or_face == "door") %>% 
  rbind(face_contenders) %>% 
  mutate(door0_or_face1 = case_when(
    door_or_face == "door" ~ 0, 
    door_or_face == "face" ~ 1, 
  ))

## Make sure this is coded right
table(contenders_facesfinalized$door_or_face, contenders_facesfinalized$door0_or_face1)

## Which types should we match to make sure we have an equal number of each?
## Median of each
contenders_facesfinalized %>% 
  group_by(gender) %>% 
  summarize(general_dprime = median(general_dprime), 
            highconfidence_treshold_dprime = median(highconfidence_treshold_dprime),
            highconfidence_subset_dprime = median(highconfidence_subset_dprime))

## Plotting distributions of all memorability
for (variable in dprime_list) {
  
  plot <- contenders_facesfinalized %>% 
    ggplot(aes(x=!!sym(variable))) +
    geom_histogram(binwidth=.19999, color="black", fill="thistle1") +
  facet_wrap(vars(gender))+
    theme_classic()
  
  print(plot)
}

```


# Pairing genders to ensure even groups

```{r}
contenders_facesfinalized_girlsingle <- contenders_facesfinalized %>% filter(gender %in% c("girls", "single"))
contenders_facesfinalized_girldouble <- contenders_facesfinalized %>% filter(gender %in% c("girls", "double"))
contenders_facesfinalized_boysingle <- contenders_facesfinalized %>% filter(gender %in% c("boys", "single"))
contenders_facesfinalized_boydouble <- contenders_facesfinalized %>% filter(gender %in% c("boys", "double"))
```

# Matching method 1
Note: nearest matching works perfectly fine 

```{r}
## Set up matching
match_object_girlsingle <- matchit(door0_or_face1 ~ general_dprime + highconfidence_treshold_dprime + highconfidence_subset_dprime,
                                    data = contenders_facesfinalized_girlsingle,
                                    #caliper = 0.57, ##NEW, used to be .55
                                    method = "nearest")

## Make new dataframe
matched_data_girlsingle <- match.data(match_object_girlsingle) %>% 
  arrange(door_or_face, image_type) %>% 
  mutate(use = "task")

## Should have _ per gender. YAY!!!
table(matched_data_girlsingle$gender)
```

# do the same matching with boys and double doors

```{r}
## Set up matching
match_object_boydouble <- matchit(door0_or_face1 ~ general_dprime + highconfidence_treshold_dprime + highconfidence_subset_dprime,
                                  data = contenders_facesfinalized_boydouble,
                                  #caliper = 0.57,##NEW, used to be .55
                                  method = "nearest")

## Make new dataframe
matched_data_boydouble <- match.data(match_object_boydouble) %>% 
  arrange(door_or_face, image_type) %>% 
  mutate(use = "task")

## Should have 42 per gender 
table(matched_data_boydouble$gender)
```


# OK not just binding together girl_single and boy_double

```{r}
## Binding two matched dataframes together
matched_data_girlsingle_boydouble <- matched_data_girlsingle %>% rbind(matched_data_boydouble)

#export this as a csv file
write.csv(x = matched_data_girlsingle_boydouble, file = "matched_data_girlsingle_boydouble.csv")

## What is the overall distance
summary(matched_data_girlsingle_boydouble$distance)
table(matched_data_girlsingle_boydouble$door_or_face, matched_data_girlsingle_boydouble$type)
```

#looking at confidence intervals and d prime stuff

```{r}
## General d'
var.test(general_dprime ~ door_or_face, data = matched_data_girlsingle_boydouble, paired = FALSE) #
t.test(general_dprime ~ door_or_face, data = matched_data_girlsingle_boydouble, paired = FALSE, var.equal = TRUE) #

## Threshold high confidence
var.test(highconfidence_treshold_dprime ~ door_or_face, data = matched_data_girlsingle_boydouble, paired = FALSE) #
t.test(highconfidence_treshold_dprime ~ door_or_face, data = matched_data_girlsingle_boydouble, paired = FALSE, var.equal = TRUE) #

## Subset high confidence
var.test(highconfidence_subset_dprime ~ door_or_face, data = matched_data_girlsingle_boydouble, paired = FALSE) #
t.test(highconfidence_subset_dprime ~ door_or_face, data = matched_data_girlsingle_boydouble, paired = FALSE, var.equal = TRUE) #
```



```{r}
summary(aov(general_dprime ~ gender, data = matched_data_girlsingle_boydouble))
kruskal.test(general_dprime ~ gender, data = matched_data_girlsingle_boydouble)

summary(aov(highconfidence_treshold_dprime ~ gender, data = matched_data_girlsingle_boydouble))
kruskal.test(highconfidence_treshold_dprime ~ gender, data = matched_data_girlsingle_boydouble)

summary(aov(highconfidence_subset_dprime ~ gender, data = matched_data_girlsingle_boydouble))
kruskal.test(highconfidence_subset_dprime ~ gender, data = matched_data_girlsingle_boydouble)
```


# Looking at final distributions

```{r}
## NOTE: to compare with old distributions, change dataframe to "stimuli.work"

for (variable in dprime_list) {
  plot <- matched_data_girlsingle_boydouble %>% 
    ggplot(aes(x=!!sym(variable), fill=door_or_face)) +
    geom_density(alpha=0.2)+
    theme_classic()
  print(plot)
}

## Distribution of different d' memorability scores across all images
matched_data_girlsingle_boydouble %>% 
  ggplot()+
  geom_density(aes(x = general_dprime, 
                   color = "general_dprime", fill = "general_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_treshold_dprime, 
                   color = "highconfidence_treshold_dprime", fill = "highconfidence_treshold_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  geom_density(aes(x = highconfidence_subset_dprime, 
                   color = "highconfidence_subset_dprime", fill = "highconfidence_subset_dprime"), 
               alpha = 0.1, na.rm = TRUE) +
  labs(x = "d'", y = "Density", title = "Memorability (d')") +
  theme_classic()+
  xlim(-3,3)

summary(matched_data_girlsingle_boydouble$general_dprime)
summary(stimuli.work$general_dprime)
```

table(matched_data_girlsingle_boydouble$image_type)
table(matched_data_girlsingle_boydouble$door_or_face)


